### 2023-12-05 main.tex
ll

@@

	The boundary Hamiltonians $H_{\text{left}}^{'}$ and $H_{\text{right}}^{'}$ relates to the transposed of  $\widetilde{H}_{\text{left}}$ and $\widetilde{H}_{\text{right}}$, i.e. to the transposed of the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}. They are obtained replacing the  extra-site bosonic creation operators $(\mathbf{a}^{+})_{a}^{0}$  (resp. $(\mathbf{a}^{+})_{a}^{L+1}$) with the corresponding reservoir parameters $\alpha_a$ (resp. $\beta_a$).

@@

We introduce
\begin{align} 
	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}\right)}\dt\label{S2Gen}
\end{align}
and
 \begin{equation}
 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
which denotes $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$. By taking the product over the chain we obtain 
\begin{equation}\label{S2-Whole}
	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
\end{equation}
We define 
\begin{equation}\label{HSecond}
	H^{''}=H_{\text{left}}^{''}+H_{\text{bulk}}+H_{\text{right}}^{''}\co
\end{equation}
that is related to $H'$ by
\begin{equation}
	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
\end{equation}
The boundary Hamiltonians of $H^{''}$ reads
\begin{align}\label{tri-diag-boundaryHamiltonians}
	H_{\text{left}}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{\text{right}}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
\end{align}
The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal. Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.

@@

where 
\begin{equation}
    \delta_{\tau_{x},N}:=\begin{cases}
        N\quad \text{if}\quad \tau_{x}=N\\
        0\quad \text{otherwise}
    \end{cases}\dt
\end{equation}

\paragraph{Proof of formula \eqref{ResulsBasis}}  
We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations. 
For the sake of notation we denote by
\begin{equation}
    \begin{pmatrix}
		X_{a}\\ 
		X_{N}
	\end{pmatrix}=\begin{pmatrix}
	    X_{1}\\
     \vdots\\
     X_{N}
	\end{pmatrix}\dt
\end{equation}
We define the transformed matrix product operators
\begin{equation}\label{Xtildes2b}
	\begin{pmatrix}
		\Xt_{a}\\ 
		\Xt_{N}
	\end{pmatrix} =S\begin{pmatrix}
		X_{a}\\X_{N}
	\end{pmatrix}=\begin{pmatrix} 
		X_{a}-\beta_{a}(X_{1}+\ldots+X_{N})\\
				X_{1}+\ldots +X_{N}\\
	\end{pmatrix}\dt
\end{equation}
We can also reverse the transformation by $S^{-1}$ and get back: 
\begin{equation}\label{Xes}
	\begin{pmatrix}
		X_{a}\\
		X_{N} 
	\end{pmatrix} =S^{-1}\begin{pmatrix}
		\widetilde{X}_{a}\\
		\widetilde{X}_{N}
	\end{pmatrix}=\begin{pmatrix}
		\Xt_{a}+\beta_{a}\Xt_{N}\\ 
		\beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
	\end{pmatrix}\dt
\end{equation}
Summing over $b\in \{1,\ldots,N\}$ in commutation relations \eqref{bulk} we have
\begin{equation} 
	\left[X_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}
\end{equation}
with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{N}$. 
Therefore, we obtain the commutation relations for $\Xt_{a}$ 
\begin{equation}\label{commutationsBula}
	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\co
\end{equation}
cf.~\eqref{commutationsBula2}.
Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ on the boundary vectors are given by 
\begin{equation}\label{commLEFT}
	 \langle \langle W|  \left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a}) \langle \langle W|  
	\co
\end{equation}
\begin{equation}\label{commRIGHT}
	\Xt_{a}  |V\rangle\rangle = (\alpha_{a}-\beta_{a}) |V\rangle\rangle 
	\co
\end{equation} 
cf.~\eqref{commLEFT2}.
Using the transformed operators $(\widetilde{X}_{a})_{a\in\{1,\ldots,N\}}$, the vector $|\Psi^{''}\rangle$ of the matrix product ansatz is written as
\begin{equation}\label{toDetermineTilde}
	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega^{'}} \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
	|V\rangle\rangle \,|\bm{\tau}\rangle
\end{equation}
where the normalization is given by 
\begin{align}
		Z_{L}&= \langle \langle W|  (X_{1}+\ldots+X_{N})^{L} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{L} |V\rangle\rangle \dt
\end{align}

To determine the eigenvector \eqref{toDetermineTilde}, we compute the coefficient $ \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
|V \rangle\rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
\begin{equation}\label{UsefulRelation}
	\widetilde{X}_{a}\widetilde{X}_{N}=\widetilde{X}_{N}\left((\alpha_{a}-\beta_{a})+\widetilde{X}_{a}\right)\dt
\end{equation}
Fix $ a\in \{1,\ldots,N-1\}$ and arbitrary $ \ell,n\in \mathbb{N}$. By applying the above formula \eqref{UsefulRelation} we have
\begin{align}\label{usefulRelaton-many}
	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=
	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell(\alpha_{a}-\beta_{a})\right)^{n}\dt
\end{align}

By taking the product over the sites $x$ from $1$ to $L$ we obtain 
	\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\prod_{x=1}^{L}\left(\widetilde{X}_{\tau_{x}}+(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)^{1-\delta_{\tau_{x},N}}\dt

@@

	 \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}

@@

	 \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
	|V\rangle\rangle=(1+\sum_{x=1}^{N}\delta_{\tau_{x},N})!\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\dt

@@

	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\dt

>>>>

\begin{equation}\label{eq:Hprimes}

@@

	The boundary Hamiltonians $H_{\text{left}}^{'}$ and $H_{\text{right}}^{'}$ in \eqref{eq:Hprimes} resemble the transposed of  $\widetilde{H}_{\text{left}}$ and $\widetilde{H}_{\text{right}}$, i.e. to the transposed of the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}. They can be identified  when replacing the  extra-site bosonic creation operators $(\mathbf{a}^{+})_{a}^{0}$  (resp. $(\mathbf{a}^{+})_{a}^{L+1}$) with the corresponding reservoir parameters $\alpha_a$ (resp. $\beta_a$).

@@

We introduce
\begin{align} 
	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}\right)}\dt\label{S2Gen}
\end{align}
and
 \begin{equation}
 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
which denotes $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$. By taking the product over the chain we obtain 
\begin{equation}\label{S2-Whole}
	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
\end{equation}
We define 
\begin{equation}\label{HSecond}
	H^{''}=H_{\text{left}}^{''}+H_{\text{bulk}}+H_{\text{right}}^{''}\co
\end{equation}
that is related to $H'$ by
\begin{equation}
	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
\end{equation}
The boundary Hamiltonians of $H^{''}$ read
\begin{align}\label{tri-diag-boundaryHamiltonians}
	H_{\text{left}}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{\text{right}}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
\end{align}
The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal. Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.

@@

where 
\begin{equation}
    \delta_{\tau_{x},N}:=\begin{cases}
        N\quad \text{if}\quad \tau_{x}=N\\
        0\quad \text{otherwise}
    \end{cases}\dt
\end{equation}
\todo{that's a 1 right?}

\paragraph{Proof of formula \eqref{ResulsBasis}}  
We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations. 
% For the sake of notation we denote by
% \begin{equation}
%     \begin{pmatrix}
% 		X_{a}\\ 
% 		X_{N}
% 	\end{pmatrix}=\begin{pmatrix}
% 	    X_{1}\\
%      \vdots\\
%      X_{N}
% 	\end{pmatrix}\co
% \end{equation}
We define the transformed matrix product operators
\begin{equation}\label{Xtildes2b}
	\begin{pmatrix}
		\Xt_{1}\\ 
		\vdots\\
		\Xt_{N-1}\\
		\Xt_{N}
	\end{pmatrix} =S\begin{pmatrix}
		X_{1}\\
		\vdots 
		\\
		X_{N-1}
		\\X_{N}
	\end{pmatrix}=\begin{pmatrix} 
		X_{1}-\beta_{1}(X_{1}+\ldots+X_{N})\\
		\vdots \\
		X_{N-1}-\beta_{N-1}(X_{1}+\ldots+X_{N})\\
				X_{1}+\ldots +X_{N}\\
	\end{pmatrix}\dt
\end{equation}
We can also reverse the transformation by $S^{-1}$ and get: 
\begin{equation}\label{Xes}
 X_{a}=	\Xt_{a}+\beta_{a}\Xt_{N}\,,\qquad
	X_{N} = \beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
\end{equation}
where  $ a\in \{1,\ldots,N-1\}$.

Summing over $b\in \{1,\ldots,N\}$ in commutation relations \eqref{bulk} we have
\begin{equation} 
	\left[X_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}
\end{equation}
with $\widetilde{X}_{N}= {X}_{1}+\ldots+ {X}_{N}$. 
Therefore, using \eqref{Xes}
we obtain the commutation relations for $\Xt_{a}$ 
\begin{equation}\label{commutationsBula}
	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\co
\end{equation}
for $a=1,\ldots,N-1$,
cf.~\eqref{commutationsBula2}.
Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ on the boundary vectors are given by 
\begin{equation}\label{commLEFT}
	 \langle \langle W|  \left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a}) \langle \langle W|  
	\co
\end{equation}
\begin{equation}\label{commRIGHT}
	\Xt_{a}  |V\rangle\rangle = (\alpha_{a}-\beta_{a}) |V\rangle\rangle 
	\co
\end{equation} 
for $a=1,\ldots,N-1$,
cf.~\eqref{commLEFT2}.
Using the transformed operators $(\widetilde{X}_{a})_{a\in\{1,\ldots,N\}}$, the vector $|\Psi^{''}\rangle$ of the matrix product ansatz is written as
\begin{equation}\label{toDetermineTilde}
	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega^{'}} \langle \langle W| \widetilde{X}_{\tau_{1}}\cdots \widetilde{X}_{\tau_{L}}
	|V\rangle\rangle \,|\bm{\tau}\rangle
\end{equation}
\todo{these do not commute. Introduced ordered product. Please check if ok}
where
the normalization is given by 
\begin{align}
		Z_{L}&= \langle \langle W|  (X_{1}+\ldots+X_{N})^{L} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{L} |V\rangle\rangle \dt
\end{align}

To determine the eigenvector \eqref{toDetermineTilde} in closed form, we compute the coefficients and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
\begin{equation}\label{UsefulRelation}
	\widetilde{X}_{a}\widetilde{X}_{N}=\widetilde{X}_{N}\left((\alpha_{a}-\beta_{a})+\widetilde{X}_{a}\right)\dt
\end{equation}
Fix  $ \ell,n\in \mathbb{N}$. By applying the above formula \eqref{UsefulRelation} we have
\begin{align}\label{usefulRelaton-many}
	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=
	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell(\alpha_{a}-\beta_{a})\right)^{n}\dt
\end{align}

Using \eqref{usefulRelaton-many} we obtain
	\sideset{}{'}\prod_{x=1}^L\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\sideset{}{'}\prod_{x=1}^L\left(\widetilde{X}_{\tau_{x}}+(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\co
where for convenience we introduce the ordered product
 \sideset{}{'}\prod_{x=1}^L \widetilde{X}_{\tau_{x}}= \widetilde{X}_{\tau_{1}}\cdots  \widetilde{X}_{\tau_{L}}\,.

@@

	 \langle \langle W| \widetilde{X}_{\tau_{1}}\cdots  \widetilde{X}_{\tau_{L}}

@@

	 \langle \langle W|  \widetilde{X}_{\tau_{1}}\cdots  \widetilde{X}_{\tau_{L}}
	|V\rangle\rangle=(1+\textstyle \sum_{x=1}^{N}\delta_{\tau_{x},N})!\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\dt

@@

	\left(1+\textstyle\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\dt
